% !TeX spellcheck = en_GB
\documentclass[10pt,a4paper]{scrbook}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{lipsum}
\pdfminorversion=7

%\usepackage[base=base.pdf]{dndcharactersheet}
\usepackage[base=base_alternative.pdf,alt]{dndcharactersheet}
\usepackage[base=details.pdf]{dnddetailssheet}
\usepackage[base=spells.pdf]{dndspellsheet}

\begin{document}
	\pagenumbering{gobble}

	\DndCharacterSheet{
		Character={
			Name=Murmiir Bormul,
			Class=Eldritch Knight (F) 4,
			Background=Burbuldor Noble,
			Player=Jens,
			Race=Mountain Dwarf,
			Alignment=Lawful Neutral,
			Exp=2700
		},
		Abilities={
			Strength=20, % incl. dwarf +2
			Dexterity=10,
			Constitution=17, % incl. dwarf +2
			Intelligence=16,
			Wisdom=9,
			Charisma=6
		},
		Inspiration={},
		Proficiencies={
			Constitution,
			Strength,
		},
		Skills={
			Athletics,
			History,
			Perception,
			Persuasion,
		},
		OtherProficiencies={
			Light armor, medium armor, heavy armor, shields\\
			simple weapons, martial weapons\\
			\\
			Common\\
			Dwarvish\\
			Orc\\
			\\
			Dragonchess, Smith's tools\\
		},
		Armor=\LARGE16\small+2,
		%Initiative=,
		Speed=25,
		Hitpoints={
			Maximum=40,
			Current=,
			Temporary={}
		},
		Hitdice={
			Count=4,
			Desc=d10
		},
		Weapons={
			Weapon1={
				Name=Handaxe T,
				AtkBonus=7,
				Damage=1d6+7,
				Type=slash
			},
			Weapon2={
				Name=Battleaxe,
				AtkBonus=7,
				Damage=1d8+5,
				Type=slash
			},
			Weapon3={
				Name=Battleaxe V,
				AtkBonus=7,
				Damage=1d10+5,
				Type=slash
			},
			Notes={
				V = with two hands\\
				T = thrown (60 ft. range)\\

				Handaxes:\\
				Epilogue, Bond of Mountains\\
				Frostbite (Saphire), Glory of Trials\\
				Reckoning, Corroded War Axe\\
				% Orbit

				Battleaxe:\\
				Agatha, Runed Blade of Hell's Games\\

				Weapon Bond: Epilogue, Frostbite\\
			}
		},
		Money={
			Copper=0,
			Silver=9,
			Electrum=0,
			Gold=5,
			Platin=0,
		},
		Equipment={
			fine clothes, a signet ring, a scroll of pedigree, \textbf{scroll of recommendation}, scroll case, a skin of fine wine, bedroll, traveler's clothes, 10 chalk\\
			chain mail, shield, 3 handaxes, battleaxe\\
			Staff, Saphire of the War Mage\\
			\textbf{dungeoneer's pack:} backpack, crowbar, hammer, 10 pitons, 10 torches, tinderbox, 10 rations, waterskin, 50 ft hempen rope
		},
		Traits={
			\tiny
			Despite my noble birth, I do not place myself above other folk. We all have the same blood.\\
			I face problems head-on. A simple, direct solution is the best path to success.\\
			I can stare down a hell hound without flinching.\\
		},
		Ideals={
			\tiny
			Responsibility. It is my duty to respect the authority of those above me, just as those below me must respect mine. (Lawful)\\
			Glory. I will bring glory to my family. This can only be done with an axe not with a quill.\\
		},
		Bonds={
			My honor is my life.\\
			I will do anything to recover the handaxes of my family.\\
		},
		Flaws={
			Dying an honorable death is better than shying away from a fight.\\
		},
		Features={
			\textbf{Darkvision} (60 feet)\\
			\textbf{Dwarven Resilience} (poison)\\
			\textbf{Stonecunning}\\
			\textbf{Kept in Style}\\
			% \textbf{Fighting Style}\\
			\textbf{Thrown Weapon Fighting} (FS)\\
			thrown weapons: +2 bonus damage,\\
			draw as part of the attack\\
			\textbf{Second Wind} (S/L) \textit{bonus action}\\
			regain hp = 1d10 + 4 (fighter level)\\
			\textbf{Action Surge} (S/L)\\
			\textbf{Weapon Bond} (2 handaxes)\\
			- can't be disarmed of that weapon unless incapacitated\\
			- \textit{bonus action} causing it to teleport instantly to your hand\\
			\textbf{Sharpshooter} (Feat 4th Level)\\
			on ranged weapon attacks:\\
			- no disadvantage at long range\\
			- ignore half and three-quarters cover\\
		},
		Notes={
		}
	}

	\DndDetailsSheet{
		Character={
			Age=57,
			Height=1.30 m,
			Weight=75.3 kg,
			Eyes=green,
			Skin=tan (22),
			Hair=black (red streaks),
		},
		Appearance={
			Murmiir wears a chain mail weaved into rigged travelers clothes.
			He carries a battleaxe and a shield on his back, and three handaxes on his belt, one of which has a saphire embeded into it.

			The small heavy set dwarf might appear slow and fat, but the muscles lurking underneath hs thick hide are trained and strong.

			He has emerald green eyes, quite rough tan skin, and black hair with streaks of red and grey in it.
			His wears his hair long and his breaded beard flows over the top of his belly.
			The breads are held together by fine but tough rings crafted from dwarven steel.
		},
		Backstory={
			% fearless, bolstered by the feats of his ancestors
			During his childhood his mother read him stories of their forefathers and their feats as great warriors.
			Ever since then fighting dragons and winning battles was all he has been thinking about.
			% knows what he can do and that he is good at it
			No one was surprised that he enlisted in Burbuldors military as soon as he was old enough.
			Here he spend most of his years, learning how to fight and lead troops, like a dwarf noble should.
			Not only was he trained properly, but he also has a talent for fighting and magic as it turns out.

			However, whenever his family calls upon him to perform his duty and help their trade endeavours.
			He does what is necessary, but his heart and his spare time belong to fighting for honor and glory.
			He recently discovered the adventuring guild in the city and is really tempted, but a worthy quest has yet to found.

			He wants to show his ancestors that the old dwarven ways are not yet lost.
			Hoping to be found worthy by his ancestors.
			While his family would like him to sit behind a desk and live a comfortable live by selling the riches of their mountain,
			they do not interfere with his adventures as long as their business is not negatively impacted.
		},
		Allies={
			Orga=House Bormul (Burbuldor),
			Symbol={Crest_Bormul.pdf},
			% mine cart, pickaxe, scale, mountain in background
			Left={
				The only like-minded among Murmiirs relatives is his grandfather Gremmand.
				He served in many wars for the dwarven kingdoms of the swordcoast
				and also fought along side his share of adventurers.
				Which ultimately led to him joining the famous adventuring guild.
				He as active for almost a century, but ultimately retired after the birth of his first grandson Germiir, Murmiirs older brother.
				Gremmand encouraged Murmiir to join the military and now the guild.

				% non-noble friend?
				% also a soldier cadet
				Murmiir bonds fast with his comrades of arms, especially his dwarven brothers.
				But his deepest affection belongs to Tharnik Lightfist, the first dwarf he fought side by side with.
				Tharnik is not a noble of Burbuldor and does not strive for power or wealth.
				Both of them value honor above all else.
			},
			Right={
				\textbf{Deities} (descending):\\
				% (war strategy), (all father, Forge, Knowledge)
				\textbf{Clangeddin Silverbeard}, Moradin,\\
				% mother (life, knowledge), (Combat prowess, luck in battle), (Festivity, brewing, song)
				Mya, Haela Brightaxe, Hanseath\\
			}
		},
		Traits={
			Left={
				Although he studied the tactics of his forefathers, he found that a more direct approach is often more successful.
				Specifically in dire situations long planning can cost valuable time.
				% I'm not a coward. And if I need to die it better be with an axe in my hand.
			},
			Right={
				\textbf{Kept In Style}\\
				While you are in Burbuldor, Baldurs Gate or Murann, your house sees to your everyday needs. Your name and signet are sufficient to cover most of your expenses; the inns, taverns, and festhalls you frequent are glad to record your debt and send an accounting to your family's estate to settle what you owe.\\
				This advantage enables you to live a comfortable lifestyle without having to pay 2 gp a day for it, or reduces the cost of a wealthy or aristocratic lifestyle by that amount. You may not maintain a less affluent lifestyle and use the difference as income—the benefit is a line of credit, not an actual monetary reward.
			}
		},
		Treasure={
			Left={
				\textbf{scroll of recommendation} from Gremmand Bormul
			},
			Right={
				Each of his axes has a story.

				\textbf{Epilogue} is a family heirloom and was given to Murmiir by his grandfather Gremmand, when he came of age.
				Murmiir won \textbf{Frostbite} as part of his graduation ceremony.
				\textbf{Reckoning} was part of an excavation from an collapsed mining shaft under Burbuldor.
				Once a Battle Axe used agains an ancient dragon, the partly melted and corroded axe serves him now as a handaxe.
				And \textbf{Agatha} he just won in a game of dragonchess.
			}
		}
	}

	\DndSpellSheet {
		Class=Eldritch Knight,
		Ability=Int,
		SaveDC=13,
		AtkBonus=5,
		Cantrips={
			Message\\
			Sword Burst\\
		},
		Level1={
			Slots=3,
			Spells={
				Absorb Elements\\
				Frost Fingers\\
				Shield\\
				Thunderwave\\
			}
		},
		Level2={
			Slots=0,
			Spells={
			}
		},
		Level3={
			Slots=0,
			Spells={
			}
		},
		Level4={
			Slots=0,
			Spells={
			}
		},
		Level5={
			Slots=0,
			Spells={
			}
		},
		Level6={
			Slots=0,
			Spells={
			}
		},
		Level7={
			Slots=0,
			Spells={
			}
		},
		Level8={
			Slots=0,
			Spells={
			}
		},
		Level9={
			Slots=0,
			Spells={
			}
		}
	}
\end{document}
